Topologically Equivariant \\ Artist Model

### 2025-09-05 slides/main.tex
added new fiber discussion

\graphicspath{.figures/, ../papers/figures/}

@@

\bibliography{references}

@@

\begin{frame}{Field types }
   A \textit{schema} consists of a pair $(\fnames, \sigma)$ where $\fnames$ is the set of field names and $\sigma: \fnames \rightarrow \textbf{DT}$ is a function from field name to field data type\cite{spivakSimplicialDatabases2009}

@@

\begin{frame}{Equivariant Artist}
\begin{figure}
    \includegraphics[width=\linewidth]{../paper/figures/artist_equiv.png}
\end{figure}
\end{frame}

\begin{frame}{artist composition}
    \begin{figure}
        \includegraphics[width=\linewidth]{../paper/figures/composition.pdf}
    \end{figure}
\end{frame}

>>>>

\graphicspath{.figures/, ../paper/figures/}

@@

\bibliography{../paper/references}

@@

\begin{frame}{Fiber space: Fields}
\begin{equation*}
    \resizebox{\textwidth}{!}{
    \begin{tabular}{|c|c|c|}
      \hline
       types and schema & \textcolor{fiber}{record} & \textcolor{section}{table}\\
      \hline
      \begin{tikzcd}[ampersand replacement=\&, sep=huge]
        \textcolor{total}{\mathcal{U}_\sigma} \arrow[d, "\pi_{\sigma}"', color=total, two heads] \arrow[r, dotted] \arrow[rd, dotted] \& \textcolor{total}{\mathcal{U}} \arrow[d, "\pi"', color=total, two heads] \\
        \textcolor{base}{C} \arrow[r, "\sigma"']                                                                                   \& \textcolor{base}{\texttt{DT}}
      \end{tikzcd}
    &
    \begin{tikzcd}[ampersand replacement=\&, sep=huge]
      \textcolor{total}{\mathcal{U}_{\sigma}} \arrow[d, "\pi_{\sigma}"', color=total, two heads] \\
      \textcolor{base}{C} \arrow[u, "\delement"', dashed, bend right, color=fiber]
      \end{tikzcd}
    &
    \begin{tikzcd}[ampersand replacement=\&, sep=huge]
      \dfiberc\coloneqq \textcolor{total}{\Gamma^{\pi}(\sigma)} \arrow[d, "\pi"', color=total, two heads] \\
      \dbasec \arrow[u, "\dsectionc"', dashed, bend right, color=section]
      \end{tikzcd}\\
      \hline
    \end{tabular}
    }
\end{equation*}

\begin{description}
    \item[$\textcolor{total}{\mathcal{U}}$] Space of all possible values, e.g. $\mathbb{R} \times \mathbb{R}^{+}$
    \item[$\textcolor{base}{C}$] Field names, e.g. $TEMP, PRCP$
    \item[$\textcolor{base}{\texttt{DT}}$] Data Type, e.g. $\texttt{float}$, $\texttt{PosFloat}$
\end{description} 
\end{frame}

\begin{frame}{Types and Schema }
   A \textit{schema} consists of a pair $(\fnames, \sigma)$ where $\fnames$ is the set of field names and $\sigma: \fnames \rightarrow \textbf{DT}$ is a function from field name to field data type\cite{spivakSimplicialDatabases2009}

@@

\begin{frame}{Equivariant Artist}
\begin{figure}
    \includegraphics[scale=.95, keepaspectratio]{../paper/figures/artist_equiv.pdf}
\end{figure}
\end{frame}

\begin{frame}{artist composition}
    \begin{figure}
        \includegraphics[scale=.95, keepaspectratio]{../paper/figures/composition.pdf}
    \end{figure}
\end{frame}
